\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\input{cover_page/cover_page.tex}
\clearpage
\section*{Declaration}

This is to certify that
\begin{enumerate}
\item The work contained in this thesis is original and has been done by myself under the
general supervision of my supervisor.

\item The work has not been submitted to any other Institute for any degree or diploma. However the second part of the work was also done as a part of my Complex Network Course under Dr. Animesh Mukherjee.

\item I have followed the guidelines provided by the Institute in writing the thesis.

\item I have conformed to the norms and guidelines given in the Ethical Code of Conduct
of the Institute.

\item Whenever I have used materials (data, theoretical analysis, and text) from other
sources, I have given due credit to them by citing them in the text of the thesis and
giving their details in the references.

\item Whenever I have quoted written materials from other sources, I have put them under
quotation marks and given due credit to the sources by citing them in the text of
the thesis and giving their details in the references.
\end{enumerate}
\vspace{2cm}
Sourav Sarkar,Department of Computer Science and Engineering\\
IIT Kharagpur\\
Date :\\

\clearpage
\input{introduction.tex}

\clearpage
\input{link_prediction/link_prediction.tex}

\input{opinion_dynamics/opinion_dynamics.tex}
\medskip
 
\bibliographystyle{unsrt}
\bibliography{btp_thesis}

\end{document}
